Predicting Fire Risk: \\ An Evaluation of the Fire Danger Index

### 2016-01-22 paper.tex
typo
bib fix, addtitle
updates to presentation

\begin{document}

\pagenumbering{roman}

@@

\section*{Acknowledgment}
\textit{No one who achieves success does so without acknowledging the help of others. The wise and confident acknowledge this help with gratitude. -Alfred North Whitehead
	}

I am indebted to my indefatigable supervisors Rob and Di, thank you for your endless patience.

To those who I adopted as my pseudo-supervisors Souhaib Ben-Taieb, Klaus Ackerman, Simon Angus, your help and advice was invaluable.

To my biggest supporters Earo Wang \& Christien Blencowe without your encouragement, your help and Earo's endless of chocolate this year would have been impossible.

Special thanks to Sarah Harris (Earth \& Atmosphereic Science, Monash), Hamish Clarke (UNSW), Stuart Matthews (Rural Fire Service, NSW), Musa Kilinc \& Danielle Wright (Country Fire Authority), who all contributed with data and helpful advice.

To my long suffering honours cohort, I apologise for the tears and for boring you with my data struggles, you have been the the best team to be a part of.

>>>>

\begin{document}
\maketitle

@@
